---
title       : How do attorneys rank judges?
subtitle    : a pitch presentation project for Coursera - developing data products
author      : Mike Jansen
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides


# <!-- https://datamj2.github.io/ddd_wk04_proj/#/ -->
# <style>
# 
# <!-- /* line 183, ../scss/default.scss */ -->
# slides > slide:not(.nobackground):after {
#   <!-- font-size: 12pt; -->
#   <!-- content: attr(data-slide-num) "/" attr(data-total-slides); -->
#   content: "2/5" ;
#   <!-- position: absolute; -->
#   <!-- bottom: 20px; -->
#   <!-- right: 60px; -->
#   <!-- line-height: 1.9; -->
#   <!-- color: darkred -->
# }
# </style>

--- .page2

## Ever wonder what attorneys think of judges?

- Do they think judges are fair?

- How well do they think judges know the law?

- Does the amount of contact they have with them influence their outlook?

- Which judges do they think should be retained?



## What if you had to appear in court?

- and you asked your attorney to rank the judge on a scale of 1-10

        - on fairness
        - legal knowledge
        - the number of times your attorney appeared before the judge


- what kind of judge would you be getting?

        - would your attorney think he/she is worth keeping on the bench?
<!-- <br> -->
<!-- <br> -->
<!-- <br> -->
<!-- <br> -->
<!-- --- .class #id -->

--- .page3

## Here's an app that does that!

- it's based on the ratings of state judges in the US Superior Court

- and predicts whether or not attorneys think he/she should be retained

        - based on how attorneys rated judges in different categories
        
- giving you an idea of what kind of judge is hearing your case

## Here's how it works

 - you pick one of three categories
 
 - then select a value
 
 - the app then predicts the judicial retention rating based on that category
 
 - view with or without the prediction model

--- .page4

## What do some of the ratings look like? 
```{r echo=T}
head(USJudgeRatings)
```

- Judge's name is in the left column

- the predictors used in the app are 

        - CONT: number of attorney contacts with the judge
        - INTG: judge's integrity, rated by attorneys
        - FAMI: judge's familiarity with the law, rated by attorney's

        


--- .page5

## Here's a sample plot from the app
```{r echo=F}
m1<-lm(RTEN ~ FAMI, data = USJudgeRatings)
labx="rating: judge's familiarity with law"
clr<-"green"
plot(USJudgeRatings$FAMI,USJudgeRatings$RTEN,xlab = labx, 
                     ylab = "ranking: worth of retention",  pch = 16, col=clr,xlim = c(5.5, 10.5), ylim = c(4, 11)) 
                abline(m1,col=clr,lwd=2)
                legend(9.5,5,c("data","Model"),pch=c(16,NA),lty=c(NA,1),lwd=c(NA,2),col=c("green","green"))
```

